I would like to express my sincere, deepest gratitude to my advisor, Donald E. Porter. During the past six and half years, Don has stood by me at every up and down, giving me every bit of his support. He has indulged me with incredible patience, and invested enormous time and energy to guide me finishing this dissertation.
Moreover, he has very kindly provided advice and recommendation to help me pursue my academic career. He has always been an inspiration and a role model to me. I cannot thank him enough for all the influence he has on me.

I would also like to thank my committee, R. Sekar, Michael Ferdman, and Timothy Roscoe. Their suggestions are inspirational and insightful. I especially appreciate the committee for having waited patiently for fifteen months after the thesis proposal, allowing me to take my pace and finish the thesis writing.

It is also an honor to work alongside so many amazing collaborators. I want to thank all of my friends in the OSCAR Lab: William Jannen, Bhushan Jain, Amogh Akshintala, Yang Zhan, Tao Zhang, and Yizheng Jiao. Each of them has offered me precious feedback and suggestion to projects in my graduate career. Also thanks for putting up with me all these years.

Special thanks go to Mona Vij, who has been both a collaborator and a good friend to me for years. She has contributed significantly to the design and promotion of Graphene-SGX. I am deeply grateful for the opportunity of working in Intel Lab with her, an opportunity that changed the fate of both me and the Graphene library OS. Mona has also helped me tremendously in pursuing my academic career. 

The Graphene library OS is a combined effort of numerous contributors. I want to thank all the graduate students and collaborators who have participated in the project: Kumar Saurabh Arora, Nehal Bandi, Jitin John, Harry A. Kalodner, Vrushali Kulkarni, Daniela Oliveira, Gurpreet Chadha, Manikantan Subramanian, Naveen Kalaskar, Thomas Mathew, Anchal Agarwal, Amit Arya, Arjun Bora, Sourabh Yerfule, Ujwala Tulshigiri, Imran Brown, Daljeet Singh Chhabra, Shahzeb Nihalahmed Patel, and Sridarshan Shetty. The project wouldn't have been successful without them.




