\section{Implementation Details in \graphene{}}
\label{sec:graphene:impl}

\paragraph{Linux \pal{}.}
The majority of \pal{} calls are simple wrappers for similar Linux system calls, 
adding less than 100 LoC on average for translation between \pal{} and Linux abstractions.
The largest \pal{} calls are for exception handling, synchronization, and picoprocess
creation, which require multiple system calls and range from 500--800 LoC each.
Creating a new picoprocesses internally requires a {\tt vfork} and {\tt exec} of a clean 
application instance, and would be more efficiently implemented in the kernel.
Finally, the other major \pal{} components are an ELF loader (2 kLoC), headers (800 LoC),
and internal support code (2.3 kLoC).

\paragraph{Alternative \pal{} Ports.}
We prove the platform independence of \graphene{}
by porting \pal{} to \emph{FreeBSD}, \emph{OSX} and \emph{Windows}.
With the alternative host \pal{}, unmodified Linux binaries,
along with {\tt glibc} and {libLinux},
can be transparently run on the host.
For FreeBSD,
only 1.2 kLoC of the host \pal{} code need to be rewritten,
which are significantly less than FreeBSD Linux compatibility module (10.8 kLoC).
\pal{} components including ELF loader and internal support code can be shared by any \pal{} ports.

%\fix{We leave host \pal{} ports to non-unix OSes like Windows as future work,
%but previous works~\cite{porter11drawbridge,baumann13bascule} have already shown it feasible.}

\begin{table}[t!b!]
\footnotesize
\centering
\begin{tabular}{|l|rr|}
\hline
{\bf Component} & {\bf Lines} & ({\bf \% Changed})\\
\hline
GNU Library C ({\tt libc}, {\tt ld}, {\tt libdl}, {\tt libpthread}) & \libclines{} & $0.07\%$ \\
\hline
Linux Library OS ({\tt libLinux}) & 31,112 & \\
Linux host \pal{} & 11,644 & \\
Extra code for Linux \sgx{} host \pal{} & 9.354 & \\
% updated by Chia-Che on Oct. 10, 2013
\hline
%Storage Server & \fixmedp{XX} & \\
Reference monitor bootstrapper & \reflines{} & \\
Linux kernel reference monitor module ({\tt /dev/graphene}) & \sandboxmodlines{} & \\
Linux kernel IPC module ({\tt /dev/gipc}) & \gipclines{} & \\
\hline
\end{tabular}
\caption[Lines of code written or changed in \graphene{}]
{Lines of code written or changed to produce \graphene{}.  Applications and other libraries are unchanged.}
\label{tab:graphene:loc}
\end{table}


%% * most calls are a wrapper, \fixmedp{XX} LoC on average.
%% * Exception handling, sync, and process creation were harder (500-800 LoC each).  Process creation requires a clean instance (vfork+exec), would be simpler to implement in kernel.
%% * Other major components: ELF loader (2kLoC), headers(800 LoC), internal support code (2300 LoC)


%\fixmedp{Chia-Che, update LoC table}

\paragraph{Implementing Linux Personality.} 
%\fixmedp{Revisit the logical flow of these paragraphs}
The \graphene{} {\tt libLinux.so} implements a subset 
of the Linux system call API (currently \graphenesyscalls{} calls)
using only the \pal{} ABI to interact with the host.
We note that Linux exports a very long tail of infrequently used calls.
%applications.
A rough analysis of this tail indicates roughly 100 additional calls that can be implemented
with the existing \pal{} ABI and coordination framework, less than 10 administrative calls that will not make sense to expose to 
an application, such as loading a kernel module or rebooting the system, and roughly 54 that will require 
\pal{} extensions to meaningfully implement, such as controlling scheduling,
NUMA placement, I/O privilege, and shared memory.
In the last category of system calls, the degree to which actual host details should be exported versus emulated is debatable.

%We believe represent the most commonly used system calls.
%When an application requests a call or argument that {\tt libLinux.so} does not implement,
%the picoprocess exits with a distinct error message. 
Each time we have tested \graphene{} with a new application, the number of extra system calls
required has dropped---most recently we only added 4 calls
(namely, epoll\_create, epoll\_wait, semget and semop)
to support the Apache web server.
Thus, we believe \graphene{} implements a representative sample of Linux calls.

%such as {\tt sched\_setparam}, which manipulates scheduler-specific
%parameters or 
%{\tt uselib}, which has been abandoned 
%in {\tt glibc} version 2 in favor of a user-space dynamic linker.
%We do not plan to implement administrative interfaces, such as {\tt reboot}.
%The growth in the set of supported system calls has been driven by 
%the requirements of new applications we use to exercise \graphene{}, and has been 
%slowing considerably over time.

%directly to guests, and thus will not implement them in {\tt libLinux.so}.

% dp: :(
\begin{comment}
Most {\tt libLinux.so} code reimplements
Linux kernel functionality.  We found it expedient to 
read the Linux source in order to understand its behavior and then reimplement 
that behavior on the \pal{} ABI in most cases.
In some cases, such as the file caching code,
%directory entry (dentry) cache, 
we refactored code directly from the Linux kernel.
%% In these cases, we simplified data structures to only include data
%% we needed for a single application, and to hook in with other 
%% {\tt libLinux} subsystems.
%% An interesting direction for future work would identify techniques
%% to automatically import larger swaths of Linux kernel code, facilitating
%% adoption of new features and bugfixes.
\end{comment}

In order to use {\tt libLinux.so}, we modified \libclines{} lines of {\tt glibc} to replace 
system instructions with function calls into {\tt lib\-Linux.so},
and to cooperatively manage thread-local storage with {\tt libLinux.so} (Table~\ref{tab:graphene:loc}).

%All totaled, we only needed to modify \libclines{} lines of glibc source code to redirect all 
%system calls to {\tt libLinux} 

\begin{comment}
\vspace{5pt}
\noindent{\bf ABI Extensions.~}
\graphene{} extends the Drawbridge ABI with 9 additional \pal{} calls.
As discussed above, one creates a new sandbox, and 
5 additional calls were added for IPC.
We also add 3 calls to manage x86 segmentation registers
and exceptions (Bascule~\cite{baumann13bascule} adds
similar extensions).
\end{comment}

\paragraph{Synchronization.} Perhaps surprisingly, implementing Linux
synchronization appears substantially easier than Windows synchronization, 
as {\tt libLinux} did not require all of the various
synchronization ABIs provided by Drawbridge.
We believe the reason for this is that Linux has consolidated 
all user-level synchronization primitives to use futexes~\cite{franke02futex},
which are essentially kernel-level wait queues.
%In Windows parlance, this is simply an Event associated with a virtual address.
%Thus, our effort implementing synchronization was relatively straightforward.

%\input{host}


