\papersection{Resource management}
\label{sec:libos:resource}


\Thelibos{}
depends on a host OS or hypervisor to manage hardware and privileged OS resources.
\Thehostabi{}
defines the abstractions managed by a host---from an I/O stream, a virtual memory area (VMAs), to a thread. %---for the development of a \libos{}.
%that are available for its guest.
These abstractions encapsulate the ubiquitously-installed hardware resources.
%, such as I/O devices, memory, and CPUs,
%to the host OSes.
Other host abstractions, %defined
%by \thehostabi{},
such as an RPC stream,
represents the low-level, privileged resources of a host OS.
%such as in-kernel queues and time sources.
\graphene{} drops the prerequisite of virtualizing %management of
any other low-level resources to run \thelibos{}
as a ubiquitous compatibility layer.
%and program \thelibos{} with the simplified, easy-to-implement host abstractions of \thehostabi{}.
%to program these resources.

%hardware and privileged OS resources,
%by encapsulating the resources as generic, user-space abstractions.
%of the host ABI.



\issuedone{1.2.a}{Discuss the role of libOS in resource management}
\thelibos{}'s role in resource management
is to allocate host abstractions
as requests %to the host
for host-managed resources.
%At a high level, the purpose of \thelibos{} is to recreate the Linux abstractions.
%\Thelibos{} implements the Linux abstractions
%based on managing the host abstractions instead of
%the underlying resources.
For instance, \thelibos{} allocates virtual pages using \thehostabi{} to request for physical pages in the host OS.
%for either usage in an application or
%internal bookkeeping,
%the implementation in
%\thelibos{} will allocate a VMA, which is the memory abstraction of \thehostabi{}, instead of physical pages.
%in a unified, guest virtual address space.
Such a \libos{} design operates on the faith that the host OS will assign physical pages to VMAs with both fairness aad efficiency.
Unless the allocation exceeds user quotas or other host-level limitations,
the \libos{} should be allowed to obtain more host-manged resources,
by increasing the allocation of a host abstraction.



A language runtime, such as a Java virtual machine~\cite{hotspot,j9,alpern2000jalapeno}, or a Python~\cite{python} or Perl~\cite{perl} runtime,
%also allocates OS-managed abstractions,
has a similar role as \thelibos{}.
%The role of \thelibos{} in resource management is close to 
%A language runtime generally relies on system APIs exported by the OSes
%for resource management.
A language runtime commonly uses existing system APIs to request for resources needed by an application.
For example, a language runtime may use \syscall{mmap} to allocate a large heap,
to assign chunks of the heap to an application.
%system calls like \syscall{mmap} to allocate a large heap,
%which is chunked into objects
%and assigned to variables in an application.
%Similar strategies have been applied to
%filesystem or threading abstractions in a language runtime. %, which %are likely to
%usually leverage the filesystem or threading APIs of the OSes.
%By managing the OS abstractions,
%exported by the OSes,
%the language runtime creates an independent view
%of system resources for applications.
%Such a design resonates with \thelibos{}. 
Therefore, the development of \thelibos{} and the development of a language runtime share
several challenges,
including bridging the gap of resource allocation models
between the guest and host
and influencing the host OS to assign hardware resources to applications efficiently.


\thelibos{} reproduces the Linux resource allocation models.
%For the portability across various host OSes,
%Since \thehostabi{} encapsulates the management of host resources,
%A primary task and challenge to managing resources in \thelibos{}
%is to reproduce the idiosyncratic %resource allocation
%features or requirements of Linux, % in Linux,
%using only the host abstractions
%defined by \thehostabi{}.
%\graphene{} also simplifies the definition of \thehostabi{},
%to include a narrowed set of host abstractions that are necessary
%for a guest environment.
%a responsibility of \thelibos{}
%is to implement different Linux models of allocating a resource.
Take page management for example.
Linux supports several ways of memory allocations, including \syscall{mmap} for allocating a fixed-size VMA, stack allocation, and \syscall{brk} for more fine-grained heap allocation.
Since \thelibos{} does not directly manage physical pages,
it requires different emulation strategies to
implement the allocation models expected by an application. %s expect when using these Linux abstractions.
A strategy %repeatedly used in \thelibos{} and language runtimes
is to ``overallocate'' certain host abstractions.
The purpose of overallocation is
to keep the flexibility of adjusting the host resources afterward from the library OS.
%The caveat of using these kinds of strategies
%is that they are based on an assumption that the host
%allocates the resources
%on demand, instead of populating the resources all at once.
%However, on some hosts, overallocation may be problematic;
%%for an environment like a \sgx{} enclave, overallocating resources such as virtual memory can still have a huge impact on resource footprints.
%for example, the current version of \sgx{} requires a static virtual memory layout,
%and each VMA is at least fully populated once at enclave creation
%for checking the integrity of memory data.
%Therefore, overallocating VMAs slows down the creation of an enclave.
%\fixme{End with a summary of the paragraph?}




%Since emulation has its cost,
%an important problem to solve in \thelibos{}








\paragraph{The comparison with alternative approaches.}
Virtualization allows guest OSes to directly manage hardware resources. % for an application.
%managing resources in a guest OS
%is to virtualize the hardware resources,
%such as memory and IO devices,
A virtual machine often runs an unmodified OS kernel,
containing drivers to manage virtualized or dedicated resources.
To fully virtual hardware resources,
a hypervisor can either emulate a virtual hardware interface,
such as QEMU~\cite{qemu}, or leverage hardware virtualization,
such as IOMMU~\cite{VT-d}.
%which allows a hypervisor
%to dedicate physical hardware resources
%to a virtual machine.
%Virtualization allows a guest OS to directly manage hardware resources, by either emulating a set of virtual hardware,
%or dedicating physical hardware to a guest OS instance.
Both virtualization strategies grant a virtual machine with direct control over hardware resource management. %managing hardware resources
%than \thelibos{} in \graphene{}.


%Compared with full virtualization, the \graphene{} approach
%The \thelibos{} design
%is similar to a para-virtualized guest OS,
%which calls out to the host OS or hypervisor for allocating resources.


Exokernel~\cite{engler95exokernel} adopts a \libos{}-like approach
to export application-level system APIs, but grants each application the privilege to directly manage hardware resources. 
%to implement the system APIs and abstractions, but allows the \libos{} to manage hardware resources directly.
The rationale behind Exokernel is to bypass the complicated kernel logics
for abstracting and multiplexing hardware resources
and provide opportunities for domain-based optimization in each application.
%Exokernel assigns available hardware resources %, such as physical pages, storage disks, and network devices, 
%to each application,
%with hardware-aided protection.
Exokernel enforces a security binding from machine resources to applications,
so that each application can
manage its own resources using an untrusted \libos{}.
The similarity between the Exokernel and \graphene{} approaches is that
they both delegate the protection and security isolation of hardware resources to the host kernel or hypervisor.


Regarding resource management,
Exokernel and \graphene{} have made different decisions for
the division of labor
between the host and \libos{}. % on managing hardware resources.
Exokernel prioritizes the efficiency of resource management for each application. 
To eliminate the overhead of multiplexing resources,
Exokernel exports the low-level hardware primitives, including physical memory, CPU, disks, TLB and page tables. 
Each \libos{} in Exokernel contains drivers to directly interfacing
these hardware primitives.
\graphene{}, on the other hand, prioritizes compatibility upon plenty of host OS and hardware platforms.
Compared with the primitives exported by Exokernel,
\thehostabi{} of \graphene{} defines abstractions
that are much more high-level and independent from the host OSes, such as files, virtual memory areas, and network sockets.
\graphene{} sacrifices the application-specific opportunities
for optimizing the resource management,
but ensures the compatibility upon any hosts with \thehostabi{}.


%Exokernel allows application-level resource management, by exposing low-level resources, such as physical pages, storage disks, and network devices, at the kernel interface.








\input{fs}
\input{network}
\input{vma}
\input{thread}






