\fixmedp{make this chapter self-contained; should be like a manual of the host ABI; avoid taking about libOS and focus on PAL}
This chapter formally defines the host ABI.
The host ABI of \graphene{} represents a specification of which OS and hardware abstractions should be implemented in the hosts, 
compared to what should be in the library OS.
%, in order to implement the library OS.
%and how to develop
%a PAL (platform adaption layer).
%which translates the host ABI
%to host OS features.
%This chapter shows how the host ABI is initially defined and extended,
%based on design principles of \graphene{}. %, including simplicity and sufficiency.
%and security isolation.
%determine the definition of the host ABI,
%as a guideline to adding host features.
%with new abstractions.
\fixmedp{A sentence on motivation might be good here.  Same with implication.  Like, what is the high level goal?  What properties would a good abi have (or how to judge goodness)?}
The purpose of the host ABI is to define
a small set of OS features,
\polish{which is both simple to port on the hosts targeted in this thesis,
and sufficient to develop a library OS
that is compatible against Linux applications for cloud or servers.}



%and 
%the design principles behind the definition, for both the simplicity of porting, and the sufficiency of implementing Linux functionality.













%ion solution (e.g., Xen) can deduplicate OS components, such as  schedulers and page fault handlers, between a host and a guest,
%by modifying the guest OS to make hypercalls into the hypervisor.



%The strategies for defining the host ABI in \graphene{}
%can be summarized as follows:
%First, \graphene{} inherits most host OS functions from \drawbridge{}~\cite{porter11drawbridge},
%with minor extensions. % for implementing Linux system calls.
%\graphene{} and \drawbridge{} share a similar motivation: reusing unmodified applications across host platforms.
%%\drawbridge{} 
%%tries to reuse Windows code
%%in most of its library OS implementation.
%%As a result, most functions defined in the \drawbridge{} host ABI have certain level of similarity with 
%%the Windows API.
%%such as the scheduling primitives.
%%\drawbridge{} makes the decision
%%primarily for maximally reusing the Windows OS code in the library OS.
%Although inheriting the host ABI from \drawbridge{} 
%is mostly an engineering decision
%in \graphene{},
%this strategy covers the typical UNIX-style OS features,
%with a definition largely distinct from Linux system calls in style.
%
%
%
%Second,
%\graphene{} adds several host functions for
%extending the library OS features which are unique to Linux.
%For example, 
%use of x86 segment registers (FS/GS) is necessary for Linux applications hard-coded with
%direct TLS (thread-local storage) references.
%The segment registers can only be written in ring 0;
%although a user-ring instruction, \code{WRFSGSBASE}, can also write to the registers,
%the feature is not opt-in on x86.
%Therefore, adding a 











%layer, which defines the entire host features
%available for implementing the library OS.
%The traditional virtual machines reuse unmodified OS kernels on a virtual hardware interface.
%Unlike a virtual machine,
%the host ABI partitions OS components into the library OS, and retains only a set of basic OS functions to interact with the hosts.
%The functions defined in the host ABI
%are either API for requesting hardware resources, or convenient features, such as scheduling primitives, which commonly exist in many OSes.
%%The functions in the host ABIs are similar to
%%the UNIX-style API, or a small portion of POSIX,
%The host ABI is selected as a pinch point for OS virtualization,
%to recycle the virtualized Linux system call implementation, and to harvest the existing host OS functionality for porting the host ABI. 
%%as a leverage point for harvesting the OS functionality implemented on the hosts.

%The \graphene{} host ABI defines a set of {\em functions}, similar to the API of UNIX or POSIX.
%The functions are directly called by the library OS, along with the arguments given either in the registers or on the stack.
%A host-specific \graphene{} loader is responsible for resolving the linking, from the library OS to the host ABI.


%\section{Formal Definition}
%
%
%This section formally defines the calling convention, data types, and functions
%in the host ABI.
%The host ABI
%specifies the scope of PAL development,
%and the host features required by the library OS.
%%The definition specifies the research problem
%%in the development of \graphene{},
%%which is the translation between the Linux system interface, the host ABI, and various host interfaces.
%



\section{PAL Subroutines}



The key component to implement the features of the host ABI
is a PAL (platform adaption layer).
The host ABI
%is not only a description of the interface to the host and library OS,
is essentially a specification of how to develop a PAL.
The specification of a PAL
includes two parts: the first is the functions used in the programming of the library OS;
the second is the calling convention
that a PAL enforces for the library OS to interact with the host ABI.
This section will discuss the PAL calling convention.



The library is loaded by the hosts as a user library.
The features of a PAL include dynamically linking the library OS
as one executable.
The host ABI avoids making assumption about the host,
including the host system call convention.
Every call from the library OS to enter the PAL is a normal function call.
To resolve function call addresses,
the PAL has to work as a dynamic loader, similar to \code{ld.so}.
Dynamic linking allows shipping the library OS as a separate binary from the host-specific PAL binaries.
%and thus can be loaded on any hosts.
%We choose to dynamically link the library OS for keeping the initialization
%adaptable to different hosts;
%For example,
%A host such as SGX can impose additional restriction on the application code to be loaded,
%including to validate a signature of application code at beginning.
%which requires all trusted code to execute in one context.
 



%to the calling convention used by the native, host system interface.
%For example, a PAL running on a Linux host
%is equivalent to a simplified version of standard C library, which contains wrappers to
%translate functions to system calls.
%Besides, the Linux PAL also works as
%a dynamic loader,
%similar to a simplified \code{ld.so},
%to bootstrap the dynamic linking between the host ABI
%and the library OS.


\fixmedp{Make this sentence more direct: "The library OS is loaded by the host OS as user libraries."}
The host ABI inherits the \graphenearch{} Linux convention. %, to simplify compilation and linking.
A PAL can load the library OS as ELF (executable and linkable format) binary~\cite{elf-format}, similar as loading a Linux library.
%The host ABI inherit the Linux calling convention,
%for the convenience of development.
%The primary architecture targeted by \graphene{} is \graphenearch{};
%The primary target of architecture in \graphene{} is x86-64;
%in the x86-64 Linux call convention,
%The host ABI follows the Linux calling convention,
%which, on the x86 architecture, passes 
%the Linux calling convention on \graphenearch{}
%specifies the arguments of a function to be passed in general-purpose registers---specifically in \code{rdi}, \code{rsi}, \code{rdx}, \code{rcx}, \code{r8}, and \code{r9}~\cite{system-v-abi}.
Inheriting the \graphenesgx{} Linux convention
simplifies the dynamic linking between the application, library OS and PAL,
and enables compiler-level optimizations for linking,
such as function name hashing.
%The host ABI also assumes the library OS to be compiled in ELF (extensible linking format).
%The decision is to match the calling conventions
%of application, library OS, and PAL,
%to allow a commodity C compiler to improve the linking procedure.
%For example, the GNU C Compiler (GCC) can optimize function name comparison
%using hashing,
%which can be simply adopted by the PAL
%if it shares a linking scheme with the library OS.
Another benefit is to simplify the debugging with GDB, which only recognizes one calling convention at a time.



%If the library OS and the hosts share the same calling convention, the PAL can directly call
%the host ABI, without any redirection.
%For other hosts,
% that do not share the calling convention with the library OS,
%such as OSX and Windows, the PALs redirect
%the function arguments to the correct registers or offsets on the stack frames assigned by the calling convention.
%Dynamic linking is beneficial for
%building a pluggable, host-independent library OS binary, and leveraging the compiler optimizations across the host ABI.





%By definition, the host ABI is limited to the OS abstractions to the local process.

%Most functions in the host ABI
%only have local effect to a picoprocess.
%Using the host ABI, the library OS can  llocate a memory region inside the current picoprocess, or create a handle that is only accessible by the current picoprocess.
%Only functions related with stream I/O
%can share OS resources with other picoprocesses, such as writing to the same file, sharing a network sockets, or connecting through a local RPC (remote-procedure call) stream.



\paragraph{Host differences.}
For a host with a different calling convention from Linux,
the PAL is responsible for translating the calling convention between the host ABI and the host system interface.
For example,
Windows and OSX have different calling conventions and binary formats
from Linux.
\fixmedp{Make this point clearer}
On all hosts, the PAL includes a simple ELF loader (even on a Linux host).
On a host like Windows or OSX, the PAL is not itself ELF,
but rather a host-specific binary that includes an ELF loader.
%therefore, a Windows PAL needs
%to swap the register values when the library OS calls the host ABI.
%Windows and OSX also accepts a different type of binary format,
%and requires the PAL to implement an ad-hoc linking scheme for the library OS as an ELF binary.




\paragraph{Error codes.}
For explicity, a function in the host ABI only returns two types of results:
a non-zero number or pointer if the function succeeds, or zero if it fails.
Unlike the Linux call convention, the host ABI does not return negative values as error codes (e.g., \code{-EINVAL}).
Instead, the host ABI delivers the failure of a function call
as an exception, with the library OS capturing the failure by an assigned exception handler.
The design is to avoid confusing
the interpretation of return values from the host ABI.



\paragraph{Dynamic linking vs static linking.}
\graphene{} dynamic links the application, library OS, and PAL
in a process.
Dynamic linking ensures the complete reuse of an unmodified application,
as well as an unmodified library OS implementation.
\graphene{} allows the binaries of application, library OS, and PAL to be deployed individually to the users,
and be swapped with different implementations.
The dynamic linking of applications is a prerequisite
to running most of the Linux applications without modification or recompilation.



However, there are cases where static linking is preferred on a host (e.g., SGX), and recompilation is acceptable to the users.
Compiling the applications, library OS, and potential a PAL
into a single binary is similar to the technique of unikernels~\cite{unikernels},
which has the benefit of compiling out unnecessary code and execution paths
from the binary. 
Theoretically, it is possible for \graphene{} to statically link an application with the library OS and a PAL,
but this technique is out of the scope of this thesis.




\section{Functions}


This section defines the functions in the host ABI, according on the type of OS features needed from a host.
This section is equivalent to a manual 
for programming the library OS against the host ABI.

